---
title: "Questioon6"
author: "Ramzan Kamoto"
date: "2024-11-27"
output: html_document
---

## Portfolio Construction 

For the final question I attempt to optimise a portfolio. 

I start by making the data monthly as suggested in the question and make returns from that. 

I then collated the two datasets. For simplicity, I only wanted to consider equities and credit instruments. So from the MAA dataset I considered everything to be credit including currencies and Rates. 

I then set up the return matrix and impute missing returns using the drawn own distribution method in order to make the matrix square. I then apply Ledoit Wolf shrinkage to my matrix and set my return vector. 

I tried to set the constraints in accordance with the questions specifications but i suspect this is where I started to have issues because my Amat and dvec were not compatible. I did check the dimentions and the length of the vector was equal to the number of rows in Amat but it did not converge. 

For this reason, I commented the optimizer to stop it from stopping the entire workflow. The remainder was adding a Roll_optimizer as in the practical with adhoc constraints just to get some inference on which indexes would be preferred under different risk types. 

```{r setup, include=FALSE}

rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful  to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

## Load data 

```{r}

maa <- read_rds("/Users/ramzankamoto/Documents/Masters/Fin Metrics/23550716fmx/data/MAA.rds")

msci <-read_rds("/Users/ramzankamoto/Documents/Masters/Fin Metrics/23550716fmx/data/msci.rds") %>% 
    filter(Name %in% c("MSCI_ACWI", "MSCI_USA", "MSCI_RE", "MSCI_Jap"))


```



```{r, echo=FALSE}
# Process Data
processed_data <- process_data_q6(maa, msci)

# Calculate Monthly Returns
maa_returns <- calculate_monthly_returns_q6(processed_data$maa)
msci_returns <- calculate_monthly_returns_q6(processed_data$msci)

# Combine Data
combined_data <- combine_data_q6(maa_returns, msci_returns)

# Make Data Wide
return_mat <- make_data_wide_q6(combined_data)

# Impute Missing Values
return_mat <- impute_missing_returns(return_mat, impute_returns_method = "Drawn_Distribution_Own")

# Covariance Matrix and Mean
return_mat_Nodate <- data.matrix(return_mat[, -1])
Sigma_LW <- RiskPortfolios::covEstimation(return_mat_Nodate, control = list(type = "lw"))
Sigma_LW <- as.matrix(Matrix::nearPD(Sigma_LW)$mat)
Mu <- return_mat %>%
  summarise(across(-date, ~prod(1 + .)^(1 / n()) - 1)) %>%
  purrr::as_vector()

# Setup Constraints
constraints <- setup_constraints(Sigma_LW, Mu)

# Optimize Portfolio
#optimal_weights <- optimize_portfolio(Sigma_LW, Mu, constraints)

# Rolling Optimization
EOM_datevec <- return_mat %>%
  select(date) %>%
  unique() %>%
  mutate(YM = format(date, "%Y-%m")) %>%
  group_by(YM) %>%
  filter(date == last(date)) %>%
  ungroup() %>%
  pull(date) %>%
  unique()

Result <- EOM_datevec %>%
  map_df(~Roll_optimizer(return_mat, EOM_date = ., LookBackSel = 36))

Result

```


