---
title: "Question2"
author: "Ramzan Kamoto"
date: "2024-11-27"
output: html_document
---

## Currency Hedging Analysis 

For question 2 I first try to replicate the plot in the paper provided to establish a negative correlation between Global returns and ZAR exchange rate. 

To do this I create a global, unhedged and hedged portfolio and ensure that the global portfolio has no local holdings. 

I then plot the scatter plot using these portfolios and fit a grey regression line to show the negative correlation. To compute the densities in the x and y axis I use the package ggMarginals from ggExtra. I struggled to make notable further improvements to the plot. 

For the statistics table I wrote a function compute_portfolio_stats to make sure all values are annualized. I suspect there was an issue with my calculations because my numbers are far off the paper. At the very least the sign global portfolio and the ZAR is negative indeed. 


```{r setup, include=FALSE}
rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)
library(ggExtra)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```



```{r}

# Load Data
Indexes <- read_rds("/Users/ramzankamoto/Documents/Masters/Fin Metrics/23550716fmx/data/Cncy_Hedge_Assets.rds") %>%
  arrange(date)

ZAR <- read_rds("/Users/ramzankamoto/Documents/Masters/Fin Metrics/23550716fmx/data/Monthly_zar.rds") %>%
  arrange(date) %>%
  mutate(value_chg = value - lag(value)) %>%
  filter(date > ymd(20020227))

# Adjust Dates
Indexes <- adjust_dates_q2(Indexes, date)
ZAR <- adjust_dates_q2(ZAR, date)

# Construct Portfolios
hedged_portfolio <- construct_hedged_portfolio_q2(Indexes, ZAR$value_chg)
unhedged_portfolio <- construct_unhedged_portfolio_q2(Indexes)
global_portfolio <- construct_global_portfolio_q2(Indexes)

# Align Data
aligned_data <- align_portfolios_q2(hedged_portfolio, unhedged_portfolio, global_portfolio, ZAR)

# Scatter Plot with Marginals
scatter_with_marginals_q2(
  aligned_data,
  x_var = value_chg,
  y_var = global,
  title = "USD-ZAR Returns vs. Global Portfolio",
  x_label = "USD-ZAR Change (%)",
  y_label = "60-40 Global Portfolio Returns (%)"
)

# Compute Portfolio Statistics
portfolio_stats <- compute_portfolio_stats_q2(aligned_data)

# Format Table for Output
stats_table <- tibble::tibble(
  Fund = c("Global (USD returns: Hedged)", 
           "Global + Local (Hedged)", 
           "Global + Local (Unhedged)"),
  `ZAR Correlation` = c(portfolio_stats$`ZAR Correlation (Global)`,
                        portfolio_stats$`ZAR Correlation (Hedged)`,
                        portfolio_stats$`ZAR Correlation (Unhedged)`),
  `Returns (Ann.)` = c(portfolio_stats$`Returns (Ann., Global)`,
                       portfolio_stats$`Returns (Ann., Hedged)`,
                       portfolio_stats$`Returns (Ann., Unhedged)`),
  `S.Dev (Ann.)` = c(portfolio_stats$`Volatility (Ann., Global)`,
                     portfolio_stats$`Volatility (Ann., Hedged)`,
                     portfolio_stats$`Volatility (Ann., Unhedged)`)
)

print(stats_table)


```

