---
title: "Question1"
author: "Ramzan Kamoto"
date: "2024-11-27"
output:
  pdf_document: default
  html_document: default
---

## Systematic AI Fund 

For this question we had to analyse our AI fund in relation to its benchmark as well as other active managers and then try to replicate the figure from Sharpe. 

I started by identifying a fund which had the median value for returns over the entire period. Note here that i did not use chaining, I simply took the mean of each active fund and took the median fund. 

I then calculate returns net of fees by adapting the fees converter function discussed during the semester. 

Finally I align my median funds returns net of fees with the AI fund and the BM. 

The density plot shows the median funds returns are highly concentrated around zero and clearly struggles to outperform the BM. 

The 12 month rolling return shows the BM and AI fund are highly correlated and in most periods the AI fund is superior. 


```{r setup, include=FALSE}

rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)
library(dplyr)
library(zoo)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

## Initialize

```{r}
# Load Data
ASISA <- read_rds("/Users/ramzankamoto/Documents/Masters/Fin Metrics/23550716fmx/data/ASISA_Rets.rds")
BM <- read_rds("/Users/ramzankamoto/Documents/Masters/Fin Metrics/23550716fmx/data/Capped_SWIX.rds")
AI_Fund <- read_rds("/Users/ramzankamoto/Documents/Masters/Fin Metrics/23550716fmx/data/AI_Max_Fund.rds")
```

## Wrangle and Plots

```{r}
# Get Median Fund
median_fund <- get_median_fund_q1(ASISA)
print(paste("Median fund is:", median_fund))

# Calculate Net Returns for Median Fund
median_fund_data <- ASISA %>%
  filter(Fund == median_fund) %>%
  calc_net_fees_q1(return_column = "Returns", fee_bps = 200)

# Align Data
aligned_data <- align_data_q1(median_fund_data, AI_Fund, BM)

# Plot Rolling Returns
plot_rolling_returns_q1(aligned_data, 
                        date_column = "date", 
                        return_columns = c("Median_Fund_Net", "AI_Fund_Return", "BM_Return"))

# Plot Rolling Density
plot_rolling_density_q1(aligned_data, 
                        date_column = "date", 
                        return_columns = c("Median_Fund_Net", "AI_Fund_Return", "BM_Return"))



```
